Learning by Teaching a Robot:\\The Case of Handwriting

### 2016-01-13 main.tex
Seriously engaging in role -> adopting role -- Pierre's suggestion

\begin{inparaenum}[\itshape 1\upshape)]
This experiment was conducted to study \item how easily children with actual
deficits take on the role of a teacher, and \item if they engage
\emph{seriously} in this role. Measuring actual handwriting improvements was
not a primary goal of this experiment.
\end{inparaenum}

@@

We only provided the children with minimal explanations on the task (they would
have to help the robot to improve its writing style), so as to assess if and how
children would naturally take on the role of the teacher. We additionally assessed
how seriously they engage into helping the robot through two additional buttons
on the tablet: a green ``thumbs up'' and a red ``thumbs down''. The children
were told to freely use them to evaluate the robot's improvements (``thumb up''
to give positive feedback, ``thumb down'' to convey negative feedback). Our
assessment builds on the hypothesis that the more the child provides feedback to
the robot, the more they assume the role of a teacher. Then, by correlating the
feedback with the actual performance of the robot, we can measure to what extent
the children are seriously assuming their role: if their feedback does correlate
with the actual performance of the robot, the child is likely engaged into a
\emph{serious} teaching role-playing.

@@

To summarize, this experiment shows that children with actual handwriting
impairments do accept well the robot, can commit themselves into long
interactions, do take on the role of the teacher (as evidenced by both the
number of writing demonstrations they provided and their self-inclination to
give feedback to the robot), and finally do usually take their teacher's role seriously.

@@

No hard conclusion can be drawn in terms of actual handwriting remediation as we
did not design this study to formally assess possible improvements. However, as
visible on Figure~\ref{fig:stimuli}, Vincent was able to significantly improve
the robot's skill, and  he acknowledged that he was the one helping the robot
during post-hoc interviews. In that respect, Vincent realized that he was ``good
enough'' at writing to help someone else. The fact that Vincent seriously
committed to the role of a teacher is further supported by feedback sent by
Vincent's parents a week after the end of the experiment: ``Vincent's
handwriting has changed over the last weeks, going from a mix of standalone and
cursive letters to full words in cursive. This requires a lot of effort and
concentration from him, but he did succeed during the sessions with the robot as
he knew he had to show a consistent style of writing to the robot''.

>>>>

\begin{inparaenum}[\itshape 1\upshape)]
This experiment was conducted to study \item how easily children with actual
deficits take on the role of a teacher, and \item if they adopt this role.
Measuring actual handwriting improvements was not a primary goal of this
experiment.
\end{inparaenum}

@@

We only provided the children with minimal explanations on the task (they would
have to help the robot to improve its writing style), so as to assess if and how
children would naturally take on the role of the teacher. We additionally assessed
how seriously they engage into helping the robot through two additional buttons
on the tablet: a green ``thumbs up'' and a red ``thumbs down''. The children
were told to freely use them to evaluate the robot's improvements (``thumb up''
to give positive feedback, ``thumb down'' to convey negative feedback). Our
assessment builds on the hypothesis that the more the child provides feedback to
the robot, the more they assume the role of a teacher. Then, by correlating the
feedback with the actual performance of the robot, we can measure to what extent
the children are adopting their teacher role: if their feedback does correlate
with the actual performance of the robot, the child has likely successfully
adopted the teacher role.

@@

To summarize, this experiment shows that children with actual handwriting
impairments do accept well the robot, can commit themselves into long
interactions, and do adopt the role of the teacher (as evidenced by both the
number of writing demonstrations they provided and their self-inclination to
give feedback to the robot).

@@

No hard conclusion can be drawn in terms of actual handwriting remediation as we
did not design this study to formally assess possible improvements. However, as
visible on Figure~\ref{fig:stimuli}, Vincent was able to significantly improve
the robot's skill, and  he acknowledged that he was the one helping the robot
during post-hoc interviews. In that respect, Vincent realized that he was ``good
enough'' at writing to help someone else. The fact that Vincent adopted
the role of a teacher is further supported by feedback sent by
Vincent's parents a week after the end of the experiment: ``Vincent's
handwriting has changed over the last weeks, going from a mix of standalone and
cursive letters to full words in cursive. This requires a lot of effort and
concentration from him, but he did succeed during the sessions with the robot as
he knew he had to show a consistent style of writing to the robot''.
